Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
Update article.tex
shorter title
say that we focus on normal-1

\section{Empirical experiments} \label{sec:results}

% Datasets
To assess our method, we have used four datasets provided by the organizers
of the Connectomics challenge : \textit{normal-1, normal-2, normal-3, normal-4}.
Those datasets have $p=1000$ time series of length $T=179500$ of image
calcium from simulated neuronal networks \citep{stetter2012model}. Those
networks have approximately 15000 edges.

>>>>

\textcolor{red}{G: Mention that correlation statistics are symmetric and do not account for direction.}

\section{Experiments} \label{sec:results}

% Datasets
To assess our method, we focus on the \textit{normal-1} dataset
provided by the organizers of the Connectomics challenge. Experiments
were also carried out on  \textit{normal-2, normal-3, normal-4} and show
similar trends.
Those datasets have $p=1000$ time series of length $T=179500$ of image
calcium from simulated neuronal networks \citep{stetter2012model}. Those
networks have approximately 15000 edges.
